DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2019-01-26 rebuttal.tex

- I'm afraid I don't understand what this means at all, could you rephrase it?
\end{mdframed}
This has been rephrased as:
\begin{mdframed}[style=manuscript] 
Likewise, down-sampling can be achieved by keeping one pixel every $n$ pixels with $n=2$ being very common.
\end{mdframed}

@@

\begin{mdframed}[style=comment] 
... is a measure of the variation of the eigenvector $\bf{u}_i$ is on the graph defined by the Laplacian L.

 - I don't think the "is" after $\bf{u}_i$ should be there.
\end{mdframed}
This has been corrected.

\begin{mdframed}[style=comment] 
Given the convolution kernel $h:\mathbb{R}_+ \to \mathbb{R}$,a signal $f\in\mathbb{R}^{N_{pix}}$ on the graph is filtered as

- You don't mention what $\mathbb{R}_+$ is or why $h$ defines that map.
\end{mdframed}
\nati{This seems clear to me. Specifying what $\mathbb{R}_+$ is would be a bit too much I believe. @all -> is it also for you?}

@@

\begin{mdframed}[style=comment] 
This localization of the kernel $h$ can be useful to visualize kernels, as explained in Appendix C.

 - Most of Appendix C is not involved with the localisation of the kernel so it might be worth expanding this sentence to "This localisation of the kernel $h$ can be useful to visualise kernels, as shown in an example of heat diffusion presented Appendix C. " Also, it is a little odd that Appendix C is mentioned before Appendix B in the text.
\end{mdframed}
We followed both of the reviewer suggestions.

@@

\begin{mdframed}[style=comment] 
However, when considering only parts of the sphere, one can observe important border effects (see Figure B.13 and Appendix B).

- I would just refer the reader to the appendix rather than the figure and the appendix. It is a bit more concise. "However, when considering only parts of the sphere, one can observe important border effects (see Appendix B)."
\end{mdframed}
We changed the manuscript according to the reviewer suggestion.

\begin{mdframed}[style=comment] 
... where $T_ig[j]=g[i-j]$ is, up to a flip, a translation operator.

 - I don't understand what you mean by a "flip", a change of sign, the inversion of the kernel?
\end{mdframed}

We updated the manuscript using:
\begin{mdframed}[style=manuscript] 
where $T_i g[j] = g[i-j]$ is, up to a flip ($g[i-j]$ instead of $g[i+j]$), a translation operator.
\end{mdframed}

@@

\begin{mdframed}[style=comment] 
Similarly as (2), the convolution of the signal $f$ by a kernel $g$ is the scalar product of $f$ with translated versions $T_ig$ of the kernel $g$.

- I think this should be "As with equation (2)" or "Similarly, as in equation (2)" but I can't tell which. Also, it would be really useful if you referred to equations by "equation (x)" rather than just "(x)" throughout - much easier to read that way.
\end{mdframed}
\todo{Assign: @michael, @tomek}
\nati{I do not know what we should do.}

@@

\begin{mdframed}[style=comment] 
The 1-neighborhood of a node is the set of nodes that are directly connected to it. The k-neighborhood of a node is the set of nodes that are connected to it through paths of length k.

- I'm a little confused here, I think the neighbourhood is every pixel which is closer than the distance of some pixel. The value of k would then be the length of the set of ordered distances for all pixels up to this pixel. Is that correct? For example, take a 3x3 square (on Euclidean space for simplicity), if the central pixel has coordinates (0, 0) then the 1-neighbourhood would be all pixels at a length of 1 pixel or less, i.e. (-1, 0), (+1, 0), (0, -1) and (0, +1) who are all at the same distance so the set of distances is {1} pixel and the length of the set is 1. The 2-neighbourhood would then be all pixels which were a distance $\sqrt{2}$ pixels or less away, i.e. (-1, 0), (+1, 0), (0, -1), (0, +1), (-1, -1), (-1, +1), (+1, -1), (+1, +1) so the set of distances would be {1, $\sqrt{2}$} pixels and the length of the set is 2. Is this correct? If so k is not a length. If this is not correct, I think I misunderstand something and so this should be updated in the text.
\end{mdframed}
\todo{Assigned: @michael}

\begin{mdframed}[style=comment] 
Similarly, each line of the matrix $\sum_{k=0}^K\theta_k\bf{L}^k$ defines an irregular patch of radius $K$.

 - What do you mean by "line"? Is it a row or a column or something else which I've misunderstood?
\end{mdframed}
We mean "column" and have corrected the manuscript.

\begin{mdframed}[style=comment] 
... where $\tilde{\bf{L}}= \frac{2}{\lambda_{max}}\bf{L}-\bf{I}=-\frac{2}{\lambda_{max}}\bf{D}^{-1/2}\bf{W}\bf{D}^{-1/2}$ is the rescaled Laplacian with eigenvalues $\tilde{\Lambda}$ in [-1, 1].

 - Could you put the equation in its own 2 line align environment to make it easier to read?
\end{mdframed}
Inspired by the reviewer suggestion, we changed the layout of that equation.

@@

\begin{mdframed}[style=comment] 
By construction of our graph, $|\mathcal{E}| < 8N_{pix}$ and the overall computational cost of the convolution reduces to $\mathcal{O}(N_{pix})$ operations. That is much more efficient than filtering with spherical harmonics, even though HEALPix was designed as an iso-latitude sampling that has a fast spherical transform.

- This could be written as "By construction of our graph, $|\mathcal{E}| < 8N_{pix}$ and the overall computational cost of the convolution reduces to $\mathcal{O}(N_{pix})$ operations and as such is much more efficient than filtering with spherical harmonics, even though HEALPix was designed as an iso-latitude sampling that has a fast spherical transform." to make it easier to read.
\end{mdframed}
Thanks for the suggestion. We changed the manuscript.

@@

\begin{mdframed}[style=comment] 
That is especially true for smooth kernels which require a low polynomial degree K.

- It is unclear what "That" refers to. If making the above change then "That" could be changed to "This" and it would make sense.
\end{mdframed}
Thanks for spotting this.

\begin{mdframed}[style=comment] 
Coarsening can be naturally designed for hierarchical pixelisation schemes, as each subdivision divides a cell in an equal number of child sub-cells.

- I think you mean "where" instead of "as"
\end{mdframed}
\todo{Assigned: @tomek}
\nati{I think the "as" is correct here. We use it for "because". Not sure...}

@@

\begin{mdframed}[style=comment] 
Coarsening is the reverse operation: merging the sub-cells toward the goal of summarizing the data supported on them.

- This has an unusual syntax which makes it difficult to follow. I think you mean something like "To coarsen, the sub-cells are merged to summarise the data supported on them."
\end{mdframed}
\todo{Assigned: @tomek}
\nati{I prefer the version we have. But I leave it up to you to decide.}

@@

\begin{mdframed}[style=comment] 
Given a map $\bf{x}\in\mathbb{R}^{N_{pix}}$, pooling defines $\bf{y}\in\mathbb{R}^{N'_{pix}}$ such as

- It should be "such that" not "such as". "Given a map $\bf{x}\in\mathbb{R}^{N_{pix}}$, pooling defines $\bf{y}\in\mathbb{R}^{N'_{pix}}$ such that"
\end{mdframed}
Thank you for spotting this mistake. We have corrected the manuscript.

@@

\begin{mdframed}[style=comment] 
... where $f$ is a function which operates on sets (possibly of varying sizes) and $N_{pix}/N'_{pix}$ is the down-sampling factor, which for HEALPix is $|\mathcal{C}(i)| = N_{pix}/N'_{pix} = (N_{side} / N'_{side})^2 = 4^p$.

- Can you explain what $p$ is and it would probably be worth splitting this equation into a multi-line align environment for clarity.
\end{mdframed}
In fact, $p$ is defined as $p=\log_2(N_{side} / N'_{side})$. We have updated the manuscript with this clarification and with an equation environnment.

@@

\begin{mdframed}[style=comment] 
The tail is composed of multiple fully connected layers (FC) followed by an optional softmax layer (SM).

- This needs to be expanded to state "The tail is composed of multiple fully connected layers (FC) followed by an optional softmax layer (SM) if the network is used for discrete classification."
\end{mdframed}
We have followed the reviewer suggestion.

\begin{mdframed}[style=comment] 
A non-linear function $\sigma(\cdot)$ is applied after every linear GC and FC layer, except for the last FC layer where it is set to the identity.

- Why specify this is identity? It could take any activation - you have already mentioned that it could be a softmax.
\end{mdframed}
We have removed the identity specification.
\begin{mdframed}[style=manuscript] 
A non-linear function $\sigma(\cdot)$ is applied after every linear $GC$ and $FC$ layer, except for the last $FC$ layer. 
\end{mdframed}

@@

\begin{mdframed}[style=comment] 
Note that the output $\bf{Y}\in\mathbb{R}^{N_{pix}\times F_{out}}$ of the last GC (or the output $\bf{Y}\in\mathbb{R}^{N_{stat}\times F_{out}}$ of the ST), ...

- What is ST, you don't mention it before and only once after?
\end{mdframed}
\todo{Assigned: @michael}

\begin{mdframed}[style=comment] 
The output’s size of the neural network depends on the task.

- It would be more correct to write "The size of the output of the neural network depends on the task."
\end{mdframed}
We agree with the reviewer and have updated the manuscript.

@@

\begin{mdframed}[style=comment] 
Its radius should be large enough to capture statistics of interest.

- I think you mean the radius of the kernel. Perhaps this could be rewritten.
\end{mdframed}
\todo{Assigned: @all}
\nati{The manuscript seems clear to me. But let me know if you think otherwise.}

@@

\begin{mdframed}[style=comment] 
For example, a small a partial sky observation can provide only limited information of cosmological relevance.

- There is just a little mix up in this sentence, maybe a copy and paste accident.
\end{mdframed}
Thanks for spotting it. We have fixed this mistake.

@@

\begin{mdframed}[style=comment] 
The cost (or loss) function $C(\bf{Y},\bar{\bf{Y}}) = C(NN_\theta(\bf{X}),\bar{\bf{Y}})$ measures how good the prediction $\bf{Y}$ is for sample $\bf{X}$, given the ground truth $\bar{\bf{Y}}$.

- This is true for supervised learning only and should be stated.
\end{mdframed}
\todo{Assigned: @michael, @nati}
\nati{In an unsupervised setting, this can just not be computed... Specifying it seems redundant to me.}

@@

\begin{mdframed}[style=comment] 
For global prediction, the cost is as if $N_{pix} = 1$.

- I think this should be "For global prediction $N_{pix} = 1$."
\end{mdframed}
\todo{Assigned: @michael}

\begin{mdframed}[style=comment] 
We emphasize that the cost function and the SM layer is the sole difference between a neural network engineered for classification or regression.

- This should be "We emphasise that the cost function and the SM layer are the sole differences between a neural network engineered for classification or regression."
\end{mdframed}
We thank the reviewer for spotting this mistake. We have updated the manuscript.
